Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-17 paper.tex
Jamie to fix less and langle in fig 2c

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-4.pdf}
      \caption{Cumulative heating}
      \label{fig:heating-4}
    \end{subfigure}
  \mycaption{Kinetic energy (a,b) \rev{and cumulative heating (c)} as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity value is $\eta=10^{-4}$
    and Figure~\ref{fig:kink_ke_log-4} is an enlarged version of
    Figure~\ref{fig:kink_ke-4}. \rev{The cumulative heating $\langle
      Q_{*} \rangle$, where $*$ is either $\nu$ for viscous heating or
      $\eta$ for Ohmic heating, is the respective heating term  
      integrated both over space and from the initial moment up to the moment $t$ in
      time. The viscous heating associated with the flute instability
      (that generated before $t\approx28$) is negligible compared to
      that associated with the kink instability (generated after
      $t\approx28$). While the isotropic 
      model permits greater viscous heating (on the order of two
      orders of magnitude), the anisotropic model enhances Ohmic
      heating.   \todo{[In 2c correct $\langle Q_{\eta} \rangle$ --
        should be LANGLE INSTEAD OF LESS SIGN]}}} 
\label{fig:kink_str8_ke-4}%
\end{figure*}

@@

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-3.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-3.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-3.pdf}
      \caption{Cumulative heat}
      \label{fig:heating_r-3}
    \end{subfigure}
\mycaption{Kinetic energy \rev{and heating} as a function of time in the cases where
$\eta=10^{-3}$.}{The results from both viscosity models are shown. The flute
instability appears earlier than where $\eta=10^{-4}$ and the growth rate of
the kink instability is decreased. \rev{The cumulative heating $\langle Q_{*} \rangle$ where $*$ is either $\nu$ for viscous heating or $\eta$ for Ohmic heating is the total heat integrated over both time and space up to a time $t$. While the heat generated via viscous heating is orders of magnitude lower when using anisotropic viscosity, Ohmic heating is enhanced by the use of the anisotropic model.}}
\label{fig:kink_str8_ke-3}%
\end{figure*}

>>>>

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-4.pdf}
      \caption{Cumulative heating}
      \label{fig:heating-4}
    \end{subfigure}
  \mycaption{Kinetic energy (a,b) \rev{and cumulative heating (c)} as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity value is $\eta=10^{-4}$
    and Figure~\ref{fig:kink_ke_log-4} is an enlarged version of
    Figure~\ref{fig:kink_ke-4}. \rev{The cumulative heating $\langle
      Q_{*} \rangle$, where $*$ is either $\nu$ for viscous heating or
      $\eta$ for Ohmic heating, is the respective heating term  
      integrated both over space and from the initial moment up to the moment $t$ in
      time. The viscous heating associated with the flute instability
      (that generated before $t\approx28$) is negligible compared to
      that associated with the kink instability (generated after
      $t\approx28$). While the isotropic 
      model permits greater viscous heating (on the order of two
      orders of magnitude), the anisotropic model enhances Ohmic
      heating.}}
\label{fig:kink_str8_ke-4}%
\end{figure*}

@@

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-3.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-3.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-3.pdf}
      \caption{Cumulative heat}
      \label{fig:heating_r-3}
    \end{subfigure}
\mycaption{Kinetic energy \rev{and heating} as a function of time in the cases where
$\eta=10^{-3}$.}{The results from both viscosity models are shown. The flute
instability appears earlier than where $\eta=10^{-4}$ and the growth rate of
the kink instability is decreased.
\rev{The cumulative heating $\langle
      Q_{*} \rangle$, where $*$ is either $\nu$ for viscous heating or
      $\eta$ for Ohmic heating, is the respective heating term  
      integrated both over space and from the initial moment up to the moment $t$ in
      time.         While the heat generated via viscous heating is
      orders of magnitude lower when using anisotropic viscosity,
      Ohmic heating is enhanced by the use of the anisotropic model.}} 
\label{fig:kink_str8_ke-3}%
\end{figure*}
